---
title: "taboo transactions across studies"
author: "Dean Baltiansky"
date: "11/9/2021"
output: pdf_document
---
# Setup
```{r}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE, message=FALSE, tidy=TRUE,
                      tidy.opts=list(width.cutoff=60))
library(ggplot2)
library(plotly)
library(dplyr)
library(knitr)
```

```{r,include=FALSE}
#load packages
if(!require(lmerTest)) install.packages("lmerTest"); require(lmerTest)
if(!require(lsr)) install.packages("lsr"); require(lsr)
if(!require(psych)) install.packages("psych"); require(psych)
if(!require(interactions)) install.packages("interactions"); require(interactions)
if(!require(jtools)) install.packages("jtools"); require(jtools)
if(!require(gridExtra)) install.packages("gridExtra"); require(gridExtra)
if(!require(see)) install.packages("see"); require(see)
if(!require(kableExtra)) install.packages("kableExtra"); require(kableExtra)
if(!require(rstatix)) install.packages("rstatix"); require(rstatix)
if(!require(apa)) install.packages("apa"); require(apa)
if(!require(apaTables)) install.packages("apaTables"); require(apaTables)
if(!require(papaja)) install.packages("papaja"); require(papaja)
if(!require(tidyverse)) install.packages("tidyverse"); require(tidyverse)

# import datasets
df_s1 <- read.csv("~/Google Drive/My Drive/taboo transactions/OSF materials/SPSP Poster 2022/data/df_s1.csv")

df_s2 <- read.csv("~/Google Drive/My Drive/taboo transactions/OSF materials/SPSP Poster 2022/data/df_s2.csv")

df_s3 <- read.csv("~/Google Drive/My Drive/taboo transactions/OSF materials/SPSP Poster 2022/data/df_s3.csv")

df_s4 <- read.csv("~/Google Drive/My Drive/taboo transactions/OSF materials/SPSP Poster 2022/data/df_s4.csv")

df_s5 <- read.csv("~/Google Drive/My Drive/taboo transactions/OSF materials/SPSP Poster 2022/data/df_s5.csv")

df_s6 <- read.csv("~/Google Drive/My Drive/taboo transactions/OSF materials/SPSP Poster 2022/data/df_s6.csv")
```

# All studies

## Combine s1-s4

```{r,include=FALSE}
# Modification of originial datasets to select columns of interests
df_ready_s1 <- df_s1 %>% 
  select(IV_taboo,personAbenefits:personBbenefits,gender,race,income,edu) %>% 
  rename(transaction = IV_taboo,
         benefits_A = personAbenefits,
         benefits_B = personBbenefits) %>% 
  mutate(transaction = ifelse(transaction == 1,"taboo","non-taboo"),
         study = "Study 1")

df_ready_s2 <- df_s2 %>% 
  select(cond,personAbenefits_taboo:personBbenefits_nonTaboo,gender,race,income,edu) %>% 
  mutate(transaction = ifelse(cond == 1,"taboo","non-taboo"),
         benefits_A = ifelse(transaction == "taboo",personAbenefits_taboo,personAbenefits_nonTaboo),
         benefits_B = ifelse(transaction == "taboo",personBbenefits_taboo,personBbenefits_nonTaboo)) %>% 
  select(transaction:benefits_B,gender,race,income,edu) %>% 
  mutate(study = "Study 2")

df_ready_s3 <- df_s3 %>% 
  select(IV2_taboo,kdny_benefit_A:car_benefit_B,gender,race,income,edu) %>% 
  mutate(benefits_A = ifelse(IV2_taboo == 1,kdny_benefit_A,car_benefit_A),
         benefits_B = ifelse(IV2_taboo == 1,kdny_benefit_B,car_benefit_B),
         transaction = ifelse(IV2_taboo == 1,"taboo","non-taboo")) %>% 
  select(transaction,benefits_A,benefits_B,gender,race,income,edu) %>% 
  mutate(study = "Study 3")

df_ready_s4 <- df_s4 %>% 
  select(cond,benefit_A,benefit_B,gender,race,income,edu) %>% 
  rename(transaction = cond,
         benefits_A = benefit_A,
         benefits_B = benefit_B) %>% 
  mutate(study = "Study 4")

df_ready_s5 <- df_s5 %>% 
  select(benefit_A,benefit_B,gender,race,income,edu) %>% 
  mutate(transaction = "taboo",
         study = "Study 5") %>% 
  rename(benefits_A = benefit_A,
         benefits_B = benefit_B) %>% 
  select(transaction,benefits_A,benefits_B,gender,race,income,edu,study)

df_ready_s6 <- df_s6 %>% 
  select(gender,race,income,edu) %>% 
  mutate(transaction = "taboo",
         study = "Study 6") %>% 
  select(transaction,gender,race,income,edu,study)

#combine the datasets and replaced NA values
df_combined <- df_ready_s1 %>% 
  bind_rows(df_ready_s2) %>% 
  bind_rows(df_ready_s3) %>% 
  bind_rows(df_ready_s4) %>% 
  bind_rows(df_ready_s5) %>% 
  bind_rows(df_ready_s6) %>% 
  mutate(study = as.factor(study),
         PID = row_number()) %>% 
  pivot_longer(benefits_A:benefits_B,
               names_to = "person",
               values_to = "benefit") %>% 
  separate(person,into = c("temp","person"),sep = "_") %>% 
  mutate(person = ifelse(study == "Study 6",NA,person)) %>% 
  mutate(Party = ifelse(person == "A","Buyer",
                        ifelse(person == "B","Seller",NA))) %>% 
  select(study,PID,transaction,Party,benefit,gender,race,income,edu)

```

## reshape s6

```{r,include=FALSE}
df_s6_long <- df_s6 %>% 
  pivot_longer(personA_short:personB_long,
               names_to = "temp",
               values_to = "benefit")  %>% 
  separate(temp,
           sep = "_",
           into = c("person","distance")) %>% 
  separate(person,into = c("temp","person"),sep = "n") %>% 
  select(-temp) %>% 
  mutate(person = ifelse(person == "A","Buyer","Seller"))
```

## Demographics

### N

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_combined %>% 
  group_by(PID) %>% 
  slice(1) %>% 
  group_by(study) %>% 
  summarise(n = n()) %>% 
  kableExtra::kable()
```

### Gender

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_combined %>% 
  group_by(PID) %>% 
  slice(1) %>% 
  ungroup() %>% 
  group_by(study,gender) %>% 
  summarise(n = n()) %>% 
  group_by(study) %>% 
  mutate(perc = 100*round(n/sum(n),4)) %>% 
  ungroup() %>% 
  mutate(gender = replace_na(gender,"other")) %>% 
  kableExtra::kable()
```

### Race

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_combined %>% 
  group_by(PID) %>% 
  slice(1) %>% 
  ungroup() %>% 
  group_by(study,race) %>% 
  summarise(n = n()) %>% 
  group_by(study) %>% 
  mutate(perc = 100*round(n/sum(n),4)) %>% 
  ungroup() %>% 
  mutate(race = replace_na(race,"other")) %>% 
  kableExtra::kable()
```

### Education

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_combined %>% 
  mutate(edu = factor(edu,c("GED",
                            "2yearColl",
                            "4yearColl",
                            "MA",
                            "PHD"))) %>% 
  group_by(PID) %>% 
  slice(1) %>% 
  ungroup() %>% 
  group_by(study,edu) %>% 
  summarise(n = n()) %>% 
  group_by(study) %>% 
  mutate(perc = 100*round(n/sum(n),4)) %>% 
  ungroup() %>% 
  filter(!is.na(edu)) %>% 
  kableExtra::kable()
```

### Income

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_combined %>% 
  mutate(income = factor(income,c("$0-$20,000",
                                  "$20,001-$40,000",
                                  "$40,001-$60,000",
                                  "$60,001-$80,000",
                                  "$80,001-$100,000",
                                  "$100,001-$120,000",
                                  "$120,001-$140,000",
                                  "$140,001-$160,000",
                                  "$160,001-$180,000",
                                  "$180,001-$200,000",
                                  "Over $200,000"))) %>% 
  group_by(PID) %>% 
  slice(1) %>% 
  ungroup() %>% 
  filter(!is.na(income)) %>% 
  ggplot(aes(x = income)) +
  geom_bar() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold",
                                   angle = 320),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  facet_wrap(~study,nrow = 2)
```

# Main effect: Taboo vs. Non-Taboo Transactions

## Descriptives

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_combined %>% 
  filter(study != "Study 5" & study != "Study 6") %>% 
  group_by(study,transaction,Party) %>% 
  summarise(M = mean(benefit),
            SD = sd(benefit)) %>% 
  kableExtra::kable()
```

## Stats

### Study 1. Two-way Repeated Measures ANOVA

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
forModel_s1 <- df_combined %>% 
  filter(study == "Study 1")

m1 <- anova_test(
  data = forModel_s1, dv = benefit, wid = PID,
  within = Party,
  between = transaction
  )

get_anova_table(m1) %>% 
  kableExtra::kable()
```

### Study 1. Post-hoc comparisons: Party

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m1a <- forModel_s1 %>%
  group_by(Party) %>%
  anova_test(dv = benefit, wid = PID, between = transaction) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m1a %>% 
  kableExtra::kable()
```

### Study 1. Post-hoc comparisons: Transaction

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m1b <- forModel_s1 %>%
  group_by(transaction) %>%
  anova_test(dv = benefit, wid = PID, within = Party) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m1b %>% 
  kableExtra::kable()
```

### Study 2. Two-way Repeated Measures ANOVA

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
forModel_s2 <- df_combined %>% 
  filter(study == "Study 2")

m2 <- anova_test(
  data = forModel_s2, dv = benefit, wid = PID,
  within = Party,
  between = transaction
  )

get_anova_table(m2) %>% 
  kableExtra::kable()
```

### Study 2. Post-hoc comparisons: Party

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m2a <- forModel_s2 %>%
  group_by(Party) %>%
  anova_test(dv = benefit, wid = PID, between = transaction) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m2a %>% 
  kableExtra::kable()
```

### Study 2. Post-hoc comparisons: Transaction

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m2b <- forModel_s2 %>%
  group_by(transaction) %>%
  anova_test(dv = benefit, wid = PID, within = Party) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m2b %>% 
  kableExtra::kable()
```

### Study 3. Two-way Repeated Measures ANOVA

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
forModel_s3 <- df_combined %>% 
  filter(study == "Study 3")

m3 <- anova_test(
  data = forModel_s3, dv = benefit, wid = PID,
  within = Party,
  between = transaction
  )

get_anova_table(m3) %>% 
  kableExtra::kable()
```

### Study 3. Post-hoc comparisons: Party

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m3a <- forModel_s3 %>%
  group_by(Party) %>%
  anova_test(dv = benefit, wid = PID, between = transaction) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m3a %>% 
  kableExtra::kable()
```

### Study 3. Post-hoc comparisons: Transaction

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m3b <- forModel_s3 %>%
  group_by(transaction) %>%
  anova_test(dv = benefit, wid = PID, within = Party) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m3b %>% 
  kableExtra::kable()
```

### Study 4. Two-way Repeated Measures ANOVA

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
forModel_s4 <- df_combined %>% 
  filter(study == "Study 4")

m4 <- anova_test(
  data = forModel_s4, dv = benefit, wid = PID,
  within = Party,
  between = transaction
  )

get_anova_table(m4) %>% 
  kableExtra::kable()
```

### Study 4. Post-hoc comparisons: Party

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m4a <- forModel_s4 %>%
  group_by(Party) %>%
  anova_test(dv = benefit, wid = PID, between = transaction) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m4a %>% 
  kableExtra::kable()
```

### Study 4. Post-hoc comparisons: Transaction

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m4b <- forModel_s4 %>%
  group_by(transaction) %>%
  anova_test(dv = benefit, wid = PID, within = Party) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m4b %>% 
  kableExtra::kable()
```

## Plot

This spits out a plot. See Figure 1 in Output folder

```{r,eval=FALSE,echo=FALSE}
png("figure1.png", width = 1800, height = 1500, bg = "transparent")
df_combined %>% 
  ggplot(aes(x = transaction,y = benefit,color = Party,fill = Party)) +
  scale_color_manual(values = c("#1C7EB5",
                                "#203864")) +
  scale_fill_manual(values = c("#1C7EB5",
                                "#203864")) +
  geom_violinhalf(position = position_nudge(0.15),
                  #fill = "gray23",
                  alpha = 0.4,
                  size = 1.2) +
  geom_jitter(alpha = 0.6,
             size = 2,
             position = position_jitter(0.15)) +
  stat_summary(fun.data = "mean_cl_boot",
               size = 2,
               geom = "errorbar",
               color = "#080807",
               position = position_dodge(width = 0.3),
               width = 0.2,
               alpha = 0.8) +
  stat_summary(fun = "mean",
               geom = "point",
               size = 8,
               position = position_dodge(width = 0.3)) +
  stat_summary(fun = "mean",
               shape = 1,
               geom = "point",
               size = 8,
               position = position_dodge(width = 0.3),
               color = "black") +
  scale_x_discrete(labels = c("taboo" = "Taboo",
                              "non-taboo" = "Non-Taboo"),
                   expand = c(0.2,.3)) +
  scale_y_continuous(limits = c(-3,3),
                     breaks = seq(-3,3,1)) +
  expand_limits(x = 2.7) +
  theme(panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", color = NA),
        legend.background = element_rect(fill = "transparent"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black",
                                   size = 46),
        axis.text.x = element_text(color = "black",
                                   face = "bold",
                                   size = 46),
        axis.title.x = element_blank(),
        axis.title.y = element_text(color = "black",
                                   face = "bold",
                                   size = 60),
        plot.title = element_text(color = "black",
                                  size = 60,
                                  face = "bold",
                                  hjust = 0.54),
        legend.title = element_text(size = 60,
                                    color = "black",
                                    face = "bold"),
        legend.text = element_text(size = 50),
        legend.position = "bottom",
        legend.key.size = unit(2,'cm')
        ) +
  facet_wrap(~study,nrow = 2) +
  theme(strip.text = element_text(size = 60,
                                  color = "#F2F2F2",
                                  face = "bold"),
        strip.background = element_rect(fill = "black"))
```

# Short or long term benefit?

## Descriptives

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s6_long %>% 
  group_by(person,distance) %>% 
  summarise(M = mean(benefit),
            SD = sd(benefit)) %>% 
  kableExtra::kable()
```

## Stats

### Two-way Repeated Measures ANOVA

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m5 <- anova_test(
  data = df_s6_long, dv = benefit, wid = PID,
  within = c(person,distance)
  )

get_anova_table(m5) %>% 
  kableExtra::kable()
```

### Post-hoc comparisons: Person

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m5a <- df_s6_long %>%
  group_by(person) %>%
  anova_test(dv = benefit, wid = PID, within = distance) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m5a %>% 
  kableExtra::kable()
```

### Post-hoc comparisons: Distance

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m5b <- df_s6_long %>%
  group_by(distance) %>%
  anova_test(dv = benefit, wid = PID, within = person) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m5b %>% 
  kableExtra::kable()
```

### Pairwise comparisons: Person

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
pwc_a <- df_s6_long %>%
  group_by(person) %>%
  pairwise_t_test(
    benefit ~ distance, paired = TRUE,
    p.adjust.method = "bonferroni"
    )

pwc_a %>% 
  kableExtra::kable()
```

### Pairwise comparisons: Distance

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
pwc_b <- df_s6_long %>%
  group_by(distance) %>%
  pairwise_t_test(
    benefit ~ person, paired = TRUE,
    p.adjust.method = "bonferroni"
    )

pwc_b %>% 
  kableExtra::kable()
```

## Plot

This spits out a plot. See Figure 2 in Output folder

```{r,eval=FALSE,echo=FALSE}

png("figure2.png", width = 1100, height = 750, bg = "transparent")
df_s6_long %>% 
  ggplot(aes(x = person,y = benefit,color = distance,fill = distance)) +
  scale_color_manual(values = c("#1C7EB5",
                                "#203864"),
                     labels = c("Long Term",
                                "Short Term")) +
  scale_fill_manual(values = c("#1C7EB5",
                                "#203864"),
                     labels = c("Long Term",
                                "Short Term")) +
  geom_violinhalf(position = position_nudge(0.15),
                  #fill = "gray23",
                  alpha = 0.4,
                  size = 1.2) +
  geom_jitter(alpha = 0.6,
             size = 2,
             position = position_jitter(0.15)) +
  stat_summary(fun.data = "mean_cl_boot",
               size = 2,
               geom = "errorbar",
               color = "#080807",
               position = position_dodge(width = 0.3),
               width = 0.2,
               alpha = 0.8) +
  stat_summary(fun = "mean",
               geom = "point",
               size = 8,
               position = position_dodge(width = 0.3)) +
  stat_summary(fun = "mean",
               shape = 1,
               geom = "point",
               size = 8,
               position = position_dodge(width = 0.3),
               color = "black") +
  scale_x_discrete(labels = c("A" = "Buyer",
                              "B" = "Seller"),
                   expand = c(0.2,.3)) +
  scale_y_continuous(limits = c(-3,3),
                     breaks = seq(-3,3,1)) +
  expand_limits(x = 2.7) +
  theme(panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", color = NA),
        legend.background = element_rect(fill = "transparent"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black",
                                   size = 46),
        axis.text.x = element_text(color = "black",
                                   face = "bold",
                                   size = 46),
        axis.title.x = element_blank(),
        axis.title.y = element_text(color = "black",
                                   face = "bold",
                                   size = 60),
        plot.title = element_text(color = "black",
                                  size = 60,
                                  face = "bold",
                                  hjust = 0.54),
        legend.title = element_blank(),
        legend.text = element_text(size = 40),
        legend.position = "right",
        legend.key.size = unit(2,'cm')
        )
```

# Intuitions about the seller

## Descriptives

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s4 %>% 
  pivot_longer(int_choice:int_ratio,
               names_to = "int",
               values_to = "value") %>% 
  group_by(cond,int) %>% 
  summarise(M = mean(value),
            SD = sd(value)) %>% 
  kableExtra::kable()
```

## Stats

### Intuition about seller: Choice

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
t_apa(t_test(int_choice ~ cond,df_s4),
      es = "cohens_d",
      es_ci = TRUE)
```

### Intuition about seller: Fully informed

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
t_apa(t_test(int_know ~ cond,df_s4),
      es = "cohens_d",
      es_ci = TRUE)
```

### Intuition about seller: Rational actor

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
t_apa(t_test(int_ratio ~ cond,df_s4),
      es = "cohens_d",
      es_ci = TRUE)
```

### Seller benefit as a function of perceived degree to which they have free choice

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m6 <- lm(benefit_B ~ cond*int_choice,df_s4)

apa_lm6 <- apa_print(m6)
apa_table(
  apa_lm6$table,
  caption = "Choice and condition predicting seller benefit",
  placement = "h",
  align = c("l","c","c","c","c")
)
```

### Seller benefit as a function of perceived degree to which they are informed

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m7 <- lm(benefit_B ~ cond*int_know,df_s4)

apa_lm7 <- apa_print(m7)
apa_table(
  apa_lm7$table,
  caption = "Informed and condition predicting seller benefit",
  placement = "h",
  align = c("l","c","c","c","c")
)
```

### Seller benefit as a function of perceived degree to which they are rational actors

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m8 <- lm(benefit_B ~ cond*int_know,df_s4)

apa_lm8 <- apa_print(m8)
apa_table(
  apa_lm8$table,
  caption = "Rational and condition predicting seller benefit",
  placement = "h",
  align = c("l","c","c","c","c")
)
```

## Plots

This spits out two plots. See Figures 3 and 4 in Output folder

```{r,eval=F,echo=F}
png("figure3.png", width = 1800, height = 600, bg = "transparent")
df_s4 %>% 
  pivot_longer(c(int_choice,int_ratio,int_know),
               names_to = "int",
               values_to = "value") %>% 
  mutate(int = ifelse(int == "int_choice","Free Choice",
                      ifelse(int == "int_know","Fully Informed",
                             ifelse(int == "int_ratio","Rational Actor",NA)))) %>% 
  ggplot(aes(x = cond,y = value,color = cond,fill = cond)) +
  scale_color_manual(values = c("#1C7EB5",
                                "#203864")) +
  scale_fill_manual(values = c("#1C7EB5",
                                "#203864")) +
  geom_violinhalf(position = position_nudge(0.15),
                  #fill = "gray23",
                  alpha = 0.4,
                  size = 1.2) +
  geom_jitter(alpha = 0.6,
             size = 2,
             position = position_jitter(0.15)) +
  stat_summary(fun.data = "mean_cl_boot",
               size = 2,
               geom = "errorbar",
               color = "#080807",
               position = position_dodge(width = 0.3),
               width = 0.2,
               alpha = 0.8) +
  stat_summary(fun = "mean",
               geom = "point",
               size = 8,
               position = position_dodge(width = 0.3)) +
  stat_summary(fun = "mean",
               shape = 1,
               geom = "point",
               size = 8,
               position = position_dodge(width = 0.3),
               color = "black") +
  scale_x_discrete(labels = c("taboo" = "Taboo",
                              "non-taboo" = "Non-Taboo"),
                   expand = c(0.2,.3)) +
  scale_y_continuous(limits = c(1,7),
                     breaks = seq(1,7,1)) +
  expand_limits(x = 2.7) +
  theme(panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", color = NA),
        legend.background = element_rect(fill = "transparent"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black",
                                   size = 46),
        axis.text.x = element_text(color = "black",
                                   face = "bold",
                                   size = 46),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(color = "black",
                                  size = 60,
                                  face = "bold",
                                  hjust = 0.54),
        legend.position = "none") +
  facet_wrap(~int,nrow = 1) +
  theme(strip.text = element_text(size = 60,
                                  color = "#F2F2F2",
                                  face = "bold"),
        strip.background = element_rect(fill = "black"))
  
```


```{r,eval=F,echo=F}
png("figure4.png", width = 1800, height = 550, bg = "transparent")
df_s4 %>% 
  pivot_longer(c(int_choice,int_ratio,int_know),
               names_to = "int",
               values_to = "value") %>% 
  mutate(int = ifelse(int == "int_choice","Free Choice",
                      ifelse(int == "int_know","Fully Informed",
                             ifelse(int == "int_ratio","Rational Actor",NA)))) %>% 
  ggplot(aes(x = value,y = benefit_B,color = cond)) +
  scale_color_manual(values = c("#1C7EB5",
                                "#203864"),
                     labels = c("Taboo",
                                "Non-Taboo")) +
  geom_point(size = 2,
             alpha = 0.6) +
  geom_smooth(method = "lm",
              size = 3) +
  scale_y_continuous(limits = c(-3,3),
                     breaks = seq(-3,3,1)) + 
  scale_x_continuous(limits = c(1,7),
                     breaks = seq(1,7,1)) +
  ylab("Seller Benefit") +
  theme(panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", color = NA),
        legend.background = element_rect(fill = "transparent"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black",
                                   size = 46),
        axis.text.x = element_text(color = "black",
                                   face = "bold",
                                   size = 46),
        axis.title.x = element_blank(),
        axis.title.y = element_text(color = "black",
                                   face = "bold",
                                   size = 40),
        plot.title = element_text(color = "black",
                                  size = 60,
                                  face = "bold",
                                  hjust = 0.54),
        legend.title = element_blank(),
        legend.text = element_text(size = 50),
        legend.position = "bottom",
        legend.key.size = unit(2,'cm')
        ) +
  facet_wrap(~int,nrow = 1) +
  theme(strip.text = element_text(size = 60,
                                  color = "#F2F2F2",
                                  face = "bold"),
        strip.background = element_rect(fill = "black"))
  
  
```

# Regulation support

## Mediation model

```{r,echo = F}
forMediation <- df_s4 %>% 
  mutate(condition = ifelse(cond == "taboo",0,1)) %>% 
  rowwise() %>% 
  mutate(regulation = mean(c(reg_buy,
                             reg_sell))) %>% 
  ungroup() %>% 
  mutate(benefit_B_z = scale(benefit_B),
         regulation_z = scale(regulation))

summary(mediate(regulation_z ~ condition + (benefit_B_z),data = forMediation))
```

